### 2021-05-24 cued/appendices.tex
Scaffold cued report

We have borrowed the priors proposed by \citet{Peixoto-Bayesian-Microcanonical} for $p(\psi | b)$. These, are repeated here for reference:
%
\begin{equation}
	p(\psi | b) = p(e | b) p(k | e, b) = \left[ \specialchoose{ \specialchoose{B}{2} }{ E} \right]^{-1} 
	\cdot \left[ \prod_r \frac{\prod_j \eta_j^r !}{n_r! q(e_r, n_r)} \right]
\end{equation}
%
Where $\specialchoose{n}{m}$ is shorthand for $\binom{n+m-1}{m} = \frac{(n+m-1)!}{(n-1)!(m)!}$ which can be thought of as the total number of distinct histograms with $n$ bins under the constraint they sum to $m$. $E = \frac{1}{2} \sum_{r,s} e_{rs}$ is the total number of edges in the graph. Importantly, $E$ is not allowed to vary and so $p(e|b)$ is uniform with respect to $e$. The variable $\eta_j^r$ is introduced to denote the number of vertices in block $r$ that have degree $j$. Formally, $\eta_j^r \coloneqq \sum_{i} \one\left\{b_i = r \right\} \one \left\{k_i = j \right\}$. Furthermore, $q(m, n)$ is the number of different histograms with at most $n$ non-zero bins that sum to $m$. $q(m, n)$ is related to but different from $\specialchoose{n}{m}$. Lastly, $e_r \coloneqq \sum_{s} e_{rs}$ is the total number of half edges in block r and $n_r \coloneqq \sum_{i} \one\{b_i = r\}$ is the number of vertices assigned to block $r$.

@@

>>>>

We have borrowed the priors proposed by \citet{Peixoto-Bayesian-Microcanonical} for $p(\psi | b)$. These, are repeated here for reference:
%
\begin{equation}
	p(\psi_e=e, \psi_k=k | b) = p(e | b) p(\psi_k | e, b) = \left[ \specialchoose{ \specialchoose{B}{2} }{ E} \right]^{-1} 
	\cdot \left[ \prod_r \frac{\prod_j \eta_j^r !}{n_r! q(e_r, n_r)} \right]
\end{equation}
%
Where $\specialchoose{n}{m}$ is shorthand for $\binom{n+m-1}{m} = \frac{(n+m-1)!}{(n-1)!(m)!}$ which can be thought of as the total number of distinct histograms with $n$ bins under the constraint they sum to $m$. $E = \frac{1}{2} \sum_{r,s} e_{rs}$ is the total number of edges in the graph. Importantly, $E$ is not allowed to vary and so $p(e|b)$ is uniform with respect to $e$. The variable $\eta_j^r$ is introduced to denote the number of vertices in block $r$ that have degree $j$. Formally, $\eta_j^r \coloneqq \sum_{i} \one\left\{b_i = r \right\} \one \left\{k_i = j \right\}$. Furthermore, $q(m, n)$ is the number of different histograms with at most $n$ non-zero bins that sum to $m$. $q(m, n)$ is related to but different from $\specialchoose{n}{m}$. Lastly, $e_r \coloneqq \sum_{s} e_{rs}$ is the total number of half edges in block r and $n_r \coloneqq \sum_{i} \one\{b_i = r\}$ is the number of vertices assigned to block $r$.

@@

\subsection{Derivation of U form}
\label{appdx:form-U}

The invariant distribution we wish to target for the $\theta$ samples is the posterior of $\theta$ given the values of the pair $(X, b)$. We write this as follows:
%
\begin{align}
	\pi_\theta(\theta) &\propto p(\theta | X, b) \propto p(b | X, \theta) p(\theta) \propto  \exp \left( - U(\theta) \right) \\
	\therefore U(\theta) &= - \left( \log p(b | X, \theta) + \log p(\theta) \right) + \textrm{const}
\end{align}
%
Where we have introduced $U(\theta)$ equal to the negative log posterior. Each of the constituent terms of $U(\theta)$ are easily computed (equation \ref{eqn:U-constituent-terms}) by defining $y_{ij} \coloneqq \one \left\{ b_i = j \right\}$ and $a_{ij} \coloneqq \phi_j(x_i; \theta)$.
%
\begin{equation}
	\log p(b | X, \theta) = \sum_{i \in [N]} \sum_{j \in [B]} y_{ij} \log a_{ij}  \quad \textrm{and} \quad
	\log p(\theta) = -\frac{(D+1)(B)}{2} \log 2\pi - \frac{1}{2 \sigma_\theta^2} || \theta ||^2
	\label{eqn:U-constituent-terms}
\end{equation}
%
Discarding constant terms, we write $U(\theta)$ as in equation \ref{eqn:U-form-appdx-0}. Note that $||\theta||^2 = \sum_{i} \theta_{i}^2 = \sum_{j=1}^{B} ||w_j||^2$ is the Euclidean norm of the vector of parameters $\theta$.
%
\begin{equation}
	U(\theta) = \left( \sum_{i=1}^{N} \sum_{j=1}^{B} y_{ij} \log \frac{1}{a_{ij}} \right)
	+ \frac{1}{2\sigma_\theta^2} ||\theta||^2 = N \cdot \Lcal(\theta) + \frac{1}{2\sigma_\theta^2} ||\theta||^2
	\label{eqn:U-form-appdx-0}
\end{equation}
%

### 2021-05-24 cued/checklist.tex
Scaffold cued report

%%% BEGIN INSTRUCTIONS %%%
The checklist follows the references.  Please
read the checklist guidelines carefully for information on how to answer these
questions.  For each question, change the default \answerTODO{} to \answerYes{},
\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
	justification to your answer}, either by referencing the appropriate section of
your paper or providing a brief inline description.  For example:
\begin{itemize}
	\item Did you include the license to the code and datasets? \answerYes{See Section gen-inst.}
	\item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
	\item Did you include the license to the code and datasets? \answerNA{}
\end{itemize}
Please do not modify the questions and only use the provided macros for your
answers.  Note that the Checklist section does not count towards the page
limit.  In your paper, please delete this instructions block and only keep the
Checklist section heading above along with the questions/answers below.
%%% END INSTRUCTIONS %%%

@@

	\item For all authors...
	\begin{enumerate}
		\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
		\answerYes{See experiments section \ref{sec:experiments}}
		\item Did you describe the limitations of your work?
		\answerYes{See conclusion \ref{sec:conclusion} and experiments \ref{sec:experiments} sections}
		\item Did you discuss any potential negative societal impacts of your work?
		\answerTODO{}
		\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
		\answerYes{}
	\end{enumerate}

@@

	\item If you ran experiments...
	\begin{enumerate}
		\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
		\answerTODO{}
		\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
		\answerYes{See appendix \ref{appdx:hyperparams}}
		\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
		\answerYes{See table \ref{tab:results}}
		\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
		\answerYes{See appendix \ref{appdx:imp-details}}
	\end{enumerate}

	\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
	\begin{enumerate}
		\item If your work uses existing assets, did you cite the creators?
		\answerYes{See section experiments \ref{sec:experiments}}
		\item Did you mention the license of the assets?
		\answerYes{See section inference \ref{sec:inference}}
		\item Did you include any new assets either in the supplemental material or as a URL?
		\answerYes{Supplementary material}
		\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
		\answerTODO{}
		\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
		\answerTODO{}
	\end{enumerate}

>>>>

@@

	\item For all authors...
	\begin{enumerate}
		\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
		\answerYes{See experiments section \ref{sec:experiments}}
		\item Did you describe the limitations of your work?
		\answerYes{See conclusion \ref{sec:conclusion} and experiments \ref{sec:experiments} sections}
		\item Did you discuss any potential negative societal impacts of your work?
		\answerYes{See conclusion \ref{sec:conclusion}}
		\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
		\answerYes{}
	\end{enumerate}

@@

	\item If you ran experiments...
	\begin{enumerate}
		\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
		\answerYes{See supplementary code}
		\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
		\answerYes{See appendix \ref{appdx:hyperparams}}
		\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
		\answerYes{See table \ref{tab:results}}
		\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
		\answerYes{See appendix \ref{appdx:imp-details}}
	\end{enumerate}

	\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
	\begin{enumerate}
		\item If your work uses existing assets, did you cite the creators?
		\answerYes{See section experiments \ref{sec:experiments}}
		\item Did you mention the license of the assets?
		\answerYes{See section inference \ref{sec:inference}}
		\item Did you include any new assets either in the supplemental material or as a URL?
		\answerYes{Supplementary material}
		\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
		\answerYes{Referred to original papers}
		\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
		\answerYes{Referred to original papers}
	\end{enumerate}
